%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{article}
\usepackage{fontspec} 
\usepackage[UTF8]{ctex}
\usepackage{epigraph}
\usepackage{titlesec}

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, left=35mm, right=25mm,top=22mm, bottom=22mm}
%, marginparsep=7pt, marginparwidth=.6in
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}
%\setCJKmainfont[BoldFont={MacFZXBSGBK.ttf}, ItalicFont={MacFZXBSGBK.ttf}, BoldItalicFont={MacFZXBSGBK.ttf}]{MacFZXBSGBK.ttf}
%\setCJKsansfont{MacFZXBSGBK.ttf}
%\setCJKmonofont{MacFZXBSGBK.ttf}


% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem}
% SET FONTS
\setCJKfamilyfont{MyCJKfzxbs}{FZXiaoBiaoSong-B05S} %方正小标宋简体
\newcommand{\fzxbs}{\CJKfamily{MyCJKfzxbs}}

\sectionfont{\fzxbs\bfseries\upshape\Large}
\subsectionfont{\fzxbs\bfseries\scshape\normalsize} 
\subsubsectionfont{\fzxbs\bfseries\upshape\large} 
%\titleformat{\section}[block]{\LARGE\bfseries}{Sec.\arabic{section}}{1em}{Hello: }[]
%\titleformat{\subsection}[block]{\Large\itshape\mdseries}{\arabic{section}.\arabic{subsection}}{1em}{}[]


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks=true, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={蔡苗 学术简历},
	pdfauthor={蔡苗},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}  
\hypersetup{linkcolor=blue, 
	citecolor = blue, 
	filecolor = black, 
	urlcolor = MidnightBlue} 



% DOCUMENT
\begin{document}
{\LARGE {\fzxbs 蔡苗}}\\[.35cm]
生物统计学博士研究生（三年级）\\
美国圣路易斯大学，公共卫生与社会正义学院，流行病与生物统计系


\section*{研究领域}
贝叶斯统计, 可靠性理论， 临床流行病学， 健康经济学， 因果推断


%\hrule
\section*{教育经历}
\noindent
\years{2017 -- 2020}美国圣路易斯大学$\;$生物统计方向$\;$公共卫生学博士\\
\years{2014 -- 2017}中国华中科技大学$\;$医院管理学方向$\;$管理学硕士\\
\years{2010 -- 2014}中国华中科技大学$\;$卫生事业管理学方向$\;$管理学学士

%\hrule
\section*{工作经历}
\noindent
\years{2019 -- 2020}美国退伍军人事务部圣路易斯分部，临床流行病学研究中心 \emph{生物统计研究员} \\
\years{2017 -- 2019}圣路易斯大学公共卫生与社会正义学院(美国国家自然科学基金资助) \emph{研究助理 } \\
\years{2016}湖北武汉雕龙数据科技有限公司 \emph{数据科学家}

%%\hrule
\section*{编程技能}
\noindent
\years{R}每日R使用者，熟练使用: \texttt{tidyverse}, \texttt{data.table}, \texttt{shiny}, \texttt{rstan}$\dots$\\
\years{Python}运用常见包进行机器学习和深度学习：\texttt{pandas}, \texttt{pyspark}, \texttt{dask}, \texttt{h2o}, \texttt{tensorflow}$\dots$\\
\years{SAS}美国退伍军人事务部全国超过20亿门诊和住院病人病历数据的处理和统计建模\\
\years{SQL}超过20亿条美国退伍军人事务部门诊和住院病历首页数据管理、数据清洗和整合




%\hrule
\section*{参与的研究项目}
\noindent
\years{2019 -- 2021}\emph{美国退伍军人事务部 Department of Veteran Affair's Health Services Research and Development Service (HSR $\&$ D)} Cause-specific mortality among users of Proton Pump Inhibitors.\\% 项目批号PPO 19-017-2
\years{2017 -- 2019}\emph{美国国家自然科学基金(National Science Foundation, NSF) }GOALI/Collaborative Research: Human Maintenance - A Prognostics Framework to Model Changes in Drivers' Safety Performance and Optimize Dispatching Policies.\\% 项目批号1635927，资助金额23万美元
\years{2015 -- 2018}\emph{中国国家自然科学基金面上项目 }基于结构方程模型的紧密型医疗联合体绩效评价以及影响因素研究\\%（项目批号：71473099）
\years{2012 -- 2015}\emph{中国国家自然科学基金面上项目 }基于病种质量管理的城市综合医院住院医疗资源利用评价模型与管理路径研究\\%（项目批号：71173081）


%%\hrule
\section*{主要荣誉 $\&$ 获奖}
\noindent
\years{2018-2020}国家留学基金委 \emph{ 国家建设高水平大学公派攻读学位博士研究生奖学金} \\%($1900$美元$\times 24$个月)
\years{2017}圣路易斯大学公共卫生与社会正义学院 \emph{博士研究生全额奖学金}\\
\years{2016}国家留学基金委 \emph{ 国家建设高水平大学公派联合培养硕士研究生奖学金} \\%($1600$美元$\times 5$个月)
\years{2013}华中科技大学 \emph{ 国家奖学金}\\
\years{2011, 2012}华中科技大学 \emph{ 国家励志奖学金}


\section*{国际同行评议期刊文章}
\noindent
\years{2018}Xiaojun Lin, \underline{Miao Cai}, Qiang Fu, et al. (2018), ``Does Hospital Competition Harm Inpatient Quality? Empirical Evidence from Shanxi, China", \emph{International Journal of Environmental Research and Public Health}. (SSCI Q1, IF: 2.468, rank: 38/164)\\
\years{2018}\underline{Miao Cai}, Echu Liu, Wei Li$^\ast$, et al. (2018), ``Rural Versus Urban Patients: Benchmarking the Outcomes of Patients with Acute Myocardial Infarction in Shanxi, China from 2013 to 2017", \emph{International Journal of Environmental Research and Public Health}. (SSCI Q1, IF: 2.468, rank: 38/164)\\
\years{2018}\underline{Miao Cai}, Echu Liu, Hongbing Tao$^\ast$, et al. (2018), ``Does A Medical Consortium Influence Health Outcomes of Hospitalized Cancer Patients? An Integrated Care Model in Shanxi, China", \emph{International Journal of Integrated Care}. (SSCI Q2, IF: 2.489, rank: 22/82)\\
\years{2018}Nan Zhang, Xiang Hu, Qiao Zhang, Peng Bai, \underline{Miao Cai}, et al. (2018), ``Non-high-density lipoprotein cholesterol to high-density lipoprotein cholesterol ratio is an independent risk factor for diabetes mellitus: results from a population-based cohort", \emph{Journal of Diabetes}. (SCI Q2, IF: 3.298, rank: 64/145)\\
\years{2017}\underline{Miao Cai}, Echu Liu, Hongbing Tao$^\ast$, et al. (2017), ``Does Level of Hospital Matter? A Study of Mortality of Acute Myocardial Infarction Patients in Shanxi, China". \emph{American Journal of Medical Quality}. (SCI Q3, IF: 1.662, rank: 69/98)\\
\years{2017}Xiaojun Lin, \underline{Miao Cai}, Hongbing Tao$^\ast$ (2017), ``Insurance status, inhospital mortality and length of stay in hospitalised patients in Shanxi, China: a cross-sectional study", \emph{BMJ open}. (SCI Q2, IF: 2.413, rank: 43/155)\\
\years{2016}Zhaohui Cheng, \underline{Miao Cai}, Hongbing Tao$^\ast$, et al. (2016), ``The efficiency and productivity measurement of rural township hospitals in China: a bootstrapping data envelopment analysis", \emph{BMJ Open}. (SCI Q1, IF: 2.369, rank: 38/155)\\
\years{2016}Xiaojun Lin, Hongbing Tao$^\ast$, \underline{Miao Cai}, et al. (2016), ``A systematic Review and Meta-analysis of the Relationship Between Hospital Volume and Outcome for Percutaneous Coronary Intervention", \emph{Medicine}. (SCI Q2, IF: 1.804, rank: 57/155)\\
\years{2015}Qin Shu, \underline{Miao Cai}, Hong-bing Tao$^\ast$, et al. (2015), ``What does a Hospital Survey on Patient Safety reveal about patient safety culture of surgical units compared with that of other units? ", \emph{Medicine}. (SCI Q2, IF: 2.133, rank: 40/155)\\
\years{2015}Zhaohui Cheng, Hongbing Tao$^\ast$, \underline{Miao Cai}, et al. (2015), ``Technical efficiency and productivity of Chinese county hospitals: an exploratory study in Henan province, China", \emph{BMJ Open}. (SCI Q1, IF: 2.562, rank: 32/155)

%\vspace{1cm}
%\vfill{}
%\hrulefill

%\begin{center}
%{\scriptsize  最新更新日期: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
%Typeset in \href{https://caimiao0714.github.io/cv/cn.pdf}{
%\fontspec{Times New Roman}
%\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
%\href{https://caimiao0714.github.io/cv/cn.pdf}{https://caimiao0714.github.io/cv/cn.pdf}}
%\end{center}

\end{document}